Name matching through deep learning

### 2018-11-19 old/paper2018/datasets.tex
fix multiply-defined labels

\begin{wrapfigure}{r}{.65\textwidth}
    \subfloat[Recall rate as a function of neighborhood size\label{people_recall}]{% 
        \includegraphics[width=.35\linewidth]{people_recall}
    }
    ~ 
    \subfloat[Mean negative distance as a function of neighborhood size\label{modified_loss}]{%
        \includegraphics[width=.35\linewidth]{people_distances}
     }
    \label{people_distances}
    \caption{Characteristics of people data}
\label{people_characteristics}
\end{wrapfigure}

@@

\begin{wrapfigure}{r}{.65\textwidth}
   \subfloat[Recall rate as a function of neighborhood size\label{company_recall}]{%
        \includegraphics[width=.35\linewidth]{company_recall}
   }
   ~
   \subfloat[Mean negative distance from anchor as a function of neighborhood size \label{modified_loss}]{%
        \includegraphics[width=.35\linewidth]{company_distances}
   }
    \label{company_distances}
    \caption{Characteristics of company data}
\label{company_characteristics}
\end{wrapfigure}

>>>>

\begin{wrapfigure}{r}{.65\textwidth}
    \subfloat[Recall rate as a function of neighborhood size\label{people_recall}]{% 
        \includegraphics[width=.35\linewidth]{people_recall}
    }
    ~ 
    \subfloat[Mean negative distance as a function of neighborhood size\label{people_distance}]{%
        \includegraphics[width=.35\linewidth]{people_distances}
     }
    \label{people_distances}
    \caption{Characteristics of people data}
\label{people_characteristics}
\end{wrapfigure}

@@

\begin{wrapfigure}{r}{.65\textwidth}
   \subfloat[Recall rate as a function of neighborhood size\label{company_recall}]{%
        \includegraphics[width=.35\linewidth]{company_recall}
   }
   ~
   \subfloat[Mean negative distance from anchor as a function of neighborhood size \label{company_distance}]{%
        \includegraphics[width=.35\linewidth]{company_distances}
   }
    \label{company_distances}
    \caption{Characteristics of company data}
\label{company_characteristics}
\end{wrapfigure}
